Parallel Global Optimization for Non-Convex Mixed-Integer Problems

### 2019-03-25 2019/RSD_Integer/RSD2019.tex

\title{A Global Optimization Algorithm for Non-Convex Mixed-Integer Problems}
\author{Victor Gergel \and Konstantin Barkalov \and Ilya Lebedev %\Letter 
\\
\email{konstantin.barkalov@itmm.unn.ru}}

@@

\section{Global search algorithm and dimension reduction}

Let us consider a multiextremal optimization problem in the form
\begin{gather}\label{problem}
\varphi(y^\ast)=\min{\left\{\varphi(y):y\in D, \; g_i(y)\leq 0, \; 1 \leq i \leq m\right\}},\\
D=\left\{y\in R^N: a_i\leq y_i \leq b_i, 1\leq i \leq N\right\}.\nonumber
\end{gather}
Suppose, that the objective function $\varphi(y)$ (henceforth denoted by $g_{m+1}(y)$) and
the left-hand sides $g_i(y), \; 1\leq i \leq m$, of the constraints satisfy the Lipschitz condition
%\[ \left|g_i(y')-g_i (y'')\right| \leq L_i \left\|y'-y'' \right\|, \; y',y''\in D, \; 1\leq i \leq m+1, \]
%with constants $L_i, \; 1 \leq i \leq m+1$, respectively,  
and may be multiextremal.

Using a continuous single-valued mapping $y(x)$  (Peano-type space-filling curve, or \textit{evolvent}) of the interval $[0,1]$ onto $D$, a multidimensional problem (\ref{problem}) can be reduced to a one-dimensional problem
\begin{equation}\label{problem1}
%\varphi(y(x^\ast))=
\min \left\{g_{m+1}(y(x)): x \in [0,1], \; g_i(y(x))\leq 0, \; 1 \leq i \leq m\right\}.
\end{equation}
The reduction of dimensionality matches the multidimensional problem with a Lipschitzian objective function and constraints with a one-dimensional problem where the respective functions satisfy the uniform H\"older condition (see \cite{Strongin2000}).

An efficient global search algorithm (GSA) for solving the constrained optimization problem 
(\ref{problem1}) has been developed at University of Nizhni Novgorod. A detailed description 
of the algorithm and the corresponding convergence theory are presented in 
\cite{Strongin2000}.

@@

Now, let us consider a method of adaptation of GSA for solving the mixed-integer global 
optimization problems 
\begin{gather}\label{problem_i}
\min{\left\{ g_{m+1}(y):y\in D, \; g_i(y)\leq 0, \; 1 \leq i \leq m\right\}},\\
D=\left\{a_i\leq y_i \leq b_i, \; 1\leq i \leq N, \; y_j \in Z, \; j \in J, \; y_i \in R, \; i \notin J \right\}.\nonumber
\end{gather}

>>>>

\title{Parallel Global Optimization for Non-Convex Mixed-Integer Problems}
\author{Konstantin Barkalov \and Ilya Lebedev %\Letter 
\\
\email{konstantin.barkalov@itmm.unn.ru}}

@@

\section{Global optimization algorithm and dimension reduction}

Let us consider a multiextremal optimization problem in the form
\begin{gather}\label{problem}
\varphi(y^\ast)=\min{\left\{\varphi(y):y\in D, \; g_j(y)\leq 0, \; 1 \leq j \leq m\right\}},\\
D=\left\{y\in R^N: a_i\leq y_i \leq b_i, 1\leq i \leq N\right\}.\nonumber
\end{gather}
Suppose, that the objective function $\varphi(y)$ (henceforth denoted by $g_{m+1}(y)$) and
the left-hand sides $g_j(y), \; 1\leq j \leq m$, of the constraints satisfy the Lipschitz condition
\[ \left|g_j(y')-g_j(y'')\right| \leq L_j \left\|y'-y'' \right\|, \; y',y''\in D, \; 1\leq j \leq m+1, \]
with constants $L_j, \; 1 \leq j \leq m+1$, respectively,  
and may be multiextremal.

Using a continuous single-valued mapping $y(x)$  (Peano-type space-filling curve, or \textit{evolvent}) of the interval $[0,1]$ onto $D$, a multidimensional problem (\ref{problem}) can be reduced to a one-dimensional problem
\begin{equation}\label{problem1}
\varphi(y(x^\ast))= \min \left\{g_{m+1}(y(x)): x \in [0,1], \; g_i(y(x))\leq 0, \; 1 \leq i \leq m\right\}.
\end{equation}
The reduction of dimensionality matches the multidimensional problem with a Lipschitzian objective function and constraints with a one-dimensional problem where the respective functions satisfy the uniform H\"older condition (see \cite{Strongin2000}).

An efficient global search algorithm (GSA) for solving the constrained optimization problem 
(\ref{problem1}) has been developed at University of Nizhni Novgorod.

%Описание индексного алгоритма

A detailed description 
of the algorithm and the corresponding convergence theory are presented in 
\cite{Strongin2000}.

@@

Now, let us consider a method of adaptation of GSA for solving the mixed-integer global 
optimization problems 
\begin{gather}\label{problem_i}
\min{\left\{ g_{m+1}(y):y\in D, \; g_j(y)\leq 0, \; 1 \leq j \leq m\right\}},\\
D=\left\{a_i\leq y_i \leq b_i, \; 1\leq i \leq N, \; y_j \in Z, \; j \in J, \; y_i \in R, \; i \notin J \right\}.\nonumber
\end{gather}
